%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
\cventry
  {Product Scientist} % Job title
  {Lion Studios by Applovin} % Organization
  {Berlin, Germany} % Location
  {Jun. 2023 - Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Promoted an A/B testing culture, ensuring \textbf{100\%} of major game changes were validated with proven results, leading to more effective data-driven decisions.}
      \item {Clustered payers into segments to identify opportunities and develop targeted offer strategies, leading to increased revenue.}
      \item {Created comprehensive user behavior reports using ML-techniques to generate hypotheses, resulting in project revenue improvements of 5-20\%.}
      \item {Generated \textbf{user behavior reports} using ML-techniques, resulting in project revenue improvements of \textbf{5-20\%} and supporting the launch of \textbf{multiple successful game updates}.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
  {Data Scientist} % Job title
  {King by ActivisionBlizzard} % Organization
  {Berlin, Germany} % Location
  {Oct. 2022 - Apr. 2023} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      % \item {Pioneered the development and implementation of AI/ML solutions for the company, resulting in \textbf{25\% increase in efficiency} and \textbf{more informed decision-making}.}
      \item {Designed and executed  A/B tests to evaluate the impact of new features and changes in the games, and \textbf{presented the results to stakeholders and management.}}
      \item {Developed and maintained dashboards and monitoring systems for level designers, utilizing integrated \textbf{ML models to provide insights and recommendations.}} % , resulting in \textbf{50\% reduction in level design time.}}
      \item {Collaborated with cross-functional teams, including game designers, developers, and product managers, to understand business needs and \textbf{identify opportunities for ML solutions.}}
    \end{cvitems}
  }


%---------------------------------------------------------
\cventry
  {Data Scientist} % Job title
  {SberGames} % Organization
  {Moscow, Russia} % Location
  {Aug. 2021 - Jul. 2022} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Fine-tuned and deployed state-of-the-art generative models.}
      \item {Created models from scratch such as: \textbf{LTV prediction, churn prediction} and 1st and 2nd purchase prediction models with  \textbf{accuracy from 70\% to 90\%.}}
      \item {Engineered a recommender system that provides personalized in-game offers that \textbf{double conversion rate (0.7\% to 1.5\%).}}
      \item {Designed A/B test - wrapping test and research costs and communicating potential value with executives.}
      \item {\textbf{Increased day 1 retention for a mobile game from 25\% to 35\%} by finding gaps in game-design using machine learning techniques.}
      % \item {Built model which predicts 7-day ARPU for a marketing campaign \textbf{with 86\% accuracy.}}
      % \item {Implemented a churn prediction to send \textbf{smart push notifications} between gaming sessions to \textbf{increase a retention rate up to 20\%.}}
      % \item {Collaborated with other departments to formulate tasks for the data science hackathon.}
    \end{cvitems}
  }

%---------------------------------------------------------
\cventry
{Data Scientist} % Job title
{BARS Group} % Organization
{Kazan, Russia} % Location
{Jun. 2018 - Aug. 2021} % Date(s)
{
  \begin{cvitems} % Description(s) of tasks/responsibilities
    \item {Trained a re-punctuation model (BERT) with \textbf{over 90\% accuracy} for the Russian language.}
    \item {Extended an open-source spell-checking project with a Russian language.}
    % \item {Developed a system for disease prediction using patient's anamnesis that is easily expandable for new diseases and prediction models.}
    \item {Trained models for symptoms extraction (NER) with good accuracy and implemented a clinical decision support system from scratch..}
    % \item {Implemented a clinical decision support system from scratch.}
  \end{cvitems}
}

%---------------------------------------------------------
% \cventry
% {Junior Data Scientist} % Job title
% {} % Organization
% {} % Location
% {Jun. 2018 - Oct. 2020} % Date(s)
% {
%   \begin{cvitems} % Description(s) of tasks/responsibilities
%     \item {Developed a system for disease prediction using patient's anamnesis that is easily expandable for new diseases and prediction models.}
%     \item {Trained models for symptoms extraction (NER) with good accuracy.}
%     \item {Implemented a clinical decision support system from scratch.}
%   \end{cvitems}
% }


%---------------------------------------------------------
  % \cventry
  %   {Lecturer (Python)} % Job title
  %   {Kazan State University} % Organization
  %   {Kazan, Russia} % Location
  %   {Sep. 2020 - Jan. 2020} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Reduced time on homework checks by 50\% by configuring Github CI/CD.}
  %       \item {Taught "Basics of Python" and "Algorithms and data structures" courses, supervised 30+ students.}
  %     \end{cvitems}
  %   }

%---------------------------------------------------------
\end{cventries}
